Embedding Intuitionistic into Classical Logic

### 2022-07-14 CSL/lipics-v2021-EIICL.tex
comments for propositional case

\begin{definition}
Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
		m&\text{if $b=a$}\\
		v(b)&\text{otherwise}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$.
		\item $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$.
		\item $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{M}$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$. We denote the set of valid formulas with CQC.
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$ and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$
	\begin{itemize}
		\item $M_u\subseteq M_w$.
		\item $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
		\item $R^{I_w}|_{M_u} = R^{I_u}$.
	\end{itemize}
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$
		\item $u, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I_u, v},\dots,t_n^{I_u, v})\in R^{I_u}$.
		\item $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$.
		\item $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. We denote the set of valid formulas with IQC.
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically.
Consider for instance the classical tautology $\varphi$ $$\neg\forall x A(x)\to \exists x \neg A(x)$$Analogous remarks with regard to validity and satisfiability hold as in the propositional case.

@@

An important step in the embedding will be the elimination of quantifiers via Herbrandization. In this process we introduce free variables and also additional function symbols to the signature. Whenever we speak of a new free variable what is meant is a free variable that does not occur in any of the considered formulas. Whenever a new function symbol is introduced we implicitly extend the signature by some not previously contained symbol.

@@

Theorem~\ref{thm:herbrand-skolem} follows from Lemmata~\ref{ap1} and~\ref{ap2} in the appendix.

@@

All that we have done is model Kripke frames with a finite number of propositional variables as a first-order theory and by definition we have

@@

\begin{example}
	Consider the law of excluded middle $$\varphi = (A\to \bot)\vee A$$ which is not intuitionistically valid. Then
	\begin{align*}
		\varphi^{C} &= K(\varphi)\to ((A\to \bot)\vee A)^u\\
		&= K(\varphi)\to (A\to \bot)^u\vee A^u\\
		&= K(\varphi)\to (\forall u'( u\preceq u' \to A^{u'}\to \bot^{u'})\vee A(u))\\
		&= K(\varphi)\to (\forall u' (u\preceq u' \to A(u')\to \bot)\vee A(u))
	\end{align*}
	and indeed $\varphi^{C}$ admits a counter model with domain $\{u, u'\}$ where $u \preceq u'$, $A(u) = 0, A(u') = 1$.
\end{example}

@@

Of course transforming a propositional formula into a predicate formula is somewhat unsatisfying. As a first step we want to apply Herbrandization. Now trying to apply it to arbitrary formulas presents us with quite a leap in complexity, leading to nested expressions that will make arguments more complicated. We therefore propose a Tseytin-like transformation that produces a formula of a more manageable syntactic form. A similar translation was proposed in~\cite{statman1979intuitionistic}.

@@

\begin{proof}
	The claims are verified in a straightforward manner by induction on the height of $\varphi$.
\end{proof}

@@

Then from the previous three Lemmas we get

@@

We are now ready to put these two reduction together with our embedding f. Let $\varphi$ be some propositional formula. As a first step we perform the normalization from the last section, i.e. instead of $\varphi$ we consider $$\varphi' = \bigwedge \mathcal S^-(\varphi)\to P_\varphi$$

Recall that since $\varphi$ is quantifier-free each formula $\psi\in\mathcal S^-(\varphi)$ is of one of the forms
$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C$$

where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u)$$
where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B(k)\wedge C(k))), \forall k(u\preceq k\to (A(k)\wedge (B(k))\to C(k)))$$
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B(k)\vee C(k))), \forall k(u\preceq k\to (A(k)\vee B(k))\to C(k))$$
$$\forall k(u\preceq k\to (\forall l(k\preceq l \to A(l)\to B(l))\to C(k)))$$
with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s)$$
where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
$$\hspace*{-2mm}\forall k(s\preceq k\to A(k)\to (B(k)\wedge C(k))), \forall k(s\preceq k\to (A(k)\wedge (B(k))\to C(k)))$$
$$\hspace*{-2mm}\forall k(s\preceq k\to A(k)\to (B(k)\vee C(k))), \forall k(s\preceq k\to (A(k)\vee (B(k))\to C(k)))$$
$$\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A(f_\psi(k))\to B(f_\psi(k)))\to C(k))$$
and $f_\psi$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model then we have a counter-model $(M',I')$ where $$M' = \{m\in M|s\preceq m\}$$ and
$$f_\psi^{I'}(u) = \begin{cases}
	f^I_\psi(u)&\text{ iff $u\preceq f^{I}_\psi(u)$}\\
	u&\text{ else}
\end{cases}$$ that is where $s$ is a least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
$$\forall k(A_\psi(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k((A_\psi(k)\wedge B_\psi(k))\to C_\psi(k))$$
$$\forall k(A_\psi(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k((A_\psi(k)\vee B_\psi(k))\to C_\psi(k))$$
$$\forall k((A_\psi(f_\psi(k))\to B_\psi(f_\psi(k)))\to C_\psi(k))$$
and $\mathcal F_\to$ denotes the set of formulas of the last kind.

This is as far as the first-order encoding can be simplified. What remains is the elimination of the remaining weak $\forall$-quantifiers.

@@

\begin{definition}
	Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^\circ$. For $\psi\in\mathcal F_\to$ we say that is it \textit{fulfilled} at $u\in M$ iff $A_\psi^I(u)\to B_\psi^I(u)$ is false or $C_\psi^I(u)$ is true. For $\psi\in\mathcal F_\to$ define $$g_\psi : M\to M, u\mapsto\begin{cases}
		u&\text{ if $\psi$ is fulfilled in $u$}\\
		f^I_\psi(u)&\text{ else}		
	\end{cases}$$Define a $\mathcal M_T = (M_T, I_T)$ as follows:
	\begin{itemize}
		\item $M_T$ is the set of sequences without repetition on $\mathcal F_\to$.
		\item Interpret $\preceq$ as the prefix-order.
		\item Have $$f_\psi^{I_T}(\psi_1\dots\psi_n) = \begin{cases}
			\psi_1\dots\psi_n&\text{if $\psi$ occurs in $\psi_1\dots\psi_n$}\\
			\psi_1\dots\psi_n\psi&\text{else}			
		\end{cases}$$
		\item For propositional variables $P$ have $$P^{I_T}(\psi_1\dots \psi_n) = P^I(g_{\psi_n}(\dots(g_{\psi_1}(s^I))\dots))$$
	\end{itemize}
\end{definition}
\begin{lemma}
	Let $\mathcal M = (M, I)$ be a counter-model to $\mathcal \varphi^\circ$.
	\begin{enumerate}
		\item $\psi$ is fulfilled at $f_\psi^I(u)$ for all $u\in M, \psi\in\mathcal F_\to$.
		\item If $\psi$ is fulfilled at some $u\in M$ then $\psi$ is fulfilled at all $w\geq u$.
	\end{enumerate}

@@

\begin{proof}
	1. If $C^I(u)$ is true then we are done due to persistency. Otherwise we know that $(A^I(f_\psi^I(u))\to B^I(f_\psi^I(u)))\to C^I(f_\psi^I(u))$ holds, so $A^I(f_\psi^I(u))\to B^I(f_\psi^I(u))$ must be true.

	2. If $C^I(u)$ is true then $C^I(w)$ is also true and we are done. So suppose $A^I(u)\to B^I(u)$ is false, i.e. $A^I(u)$ true and $B^I(u)$ false. Then due to the persistency condition $A^I(w)$ is also true. Again if $C^I(w)$ is true we are done. Otherwise we know that $B^I(f^I(w))$ must be false, since $(A^I(f^I_\psi(w))\to B^I(f^I_\psi(w)))\to C^I(w)$ and $A^I(f^I_\psi(w))$ hold. But then due to persistency so is $B^I(w)$ and we have that $\psi$ is fulfilled at $w$.
\end{proof}

Essentially what fulfilment of $\psi$ at $u$ tells us is that having $f_\psi(w) = w$ for all $w\geq u$ works.
With this lemma in hand showing that $(M_T, I_T)$ is a counter-model to $\varphi^\circ$ is a straightforward check of definitions.

@@

\begin{example}
	Consider
	$$\mathcal S = \{(A\to B)\to C, (B\to A)\to D, (A\wedge B)\to \bot, (C\vee D)\to E\}$$and $\varphi = \bigwedge S\to E$ which has the Kripke counter-model
	\begin{center}
		\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
			\node (center) {};
			\node[squarednode]      (right)   [right=of center] {$B, C$};
			\node[squarednode]      (left)    [left=of center] {$A, D$};
			\node[squarednode]      (lower)       	[below=of center] {};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left.south east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right.south west);			
		\end{tikzpicture}
	\end{center}
	\vspace*{-.3cm}where at each node the true propositions are indicated.

	There is a corresponding classical counter-model $\mathcal M = (M, I)$ to $\varphi^\circ$ with $M = \{u, u_l, u_r\}$, $A^{I}(l) = D^I(l) = B^I(r) = C^I(r) = 1$ and $0$ else.

	Denoting $\psi_1 := (A\to B)\to C$ and $\psi_2 := (A\to B)\to C$ this corresponds to a counter-model $\mathcal M_T = (M_T, I_T)$ of $\varphi^\circ$ with $M_T = \{\epsilon, \psi_1, \psi_2, \psi_1\psi_2, \psi_2\psi_1\}$ and interpretation as presented below
	\begin{center}
		\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
			\node (center) {};
			\node[squarednode]      (right1)   [right=of center] {$B, C$};
			\node[squarednode]      (right2)   [above=of right1] {$B, C$};
			\node[squarednode]      (left1)    [left=of center] {$A, D$};
			\node[squarednode]      (left2)    [above=of left1] {$A, D$};
			\node[squarednode]      (lower)       	[below=of center] {};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left1.south east) node [midway, below left] {$f_{\psi_1}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right1.south west) node [midway, below right] {$f_{\psi_2}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (left1.north) -- (left2.south) node [midway, right] {$f_{\psi_2}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (right1.north) -- (right2.south) node [midway, left] {$f_{\psi_1}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (left1.south west) to [out=225, in=135, loop, looseness=3] node [left] {$f_{\psi_1}$} (left1.north west);		
			\draw[-{Stealth[length=3mm, width=3mm]}] (right1.south east) to [out=315, in=45, loop, looseness=3] node [right] {$f_{\psi_2}$} (right1.north east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (left2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (left2.north east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (right2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (right2.north east);		
		\end{tikzpicture}
	\end{center}
\end{example}

So we know that $\varphi^\circ$ is valid iff it is valid for structures that have as a domain the sequences without repetition over $\mathcal F_\to$, ordered by the prefix-relation and $$s^I = \epsilon, f_\psi^I(x) = \begin{cases}
	x&\text{ if $\psi$ occurs in $x$}\\
	x\psi&\text{ otherwise}
\end{cases}$$ Now we can replace all $\forall$-quantifiers by enumerating all the ground terms and finally all distinct ground instances of relations by new propositional variables yielding a CPC formula. This gives us the following translation:

>>>>

\begin{definition}
Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
		m, &\text{if $b=a$,}\\
		v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$.
		\item $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$.
		\item $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{M}$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$. We denote the set of valid formulas with CQC.
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$ and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$
	\begin{itemize}
		\item $M_u\subseteq M_w$.
		\item $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
		\item $R^{I_w}|_{M_u} = R^{I_u}$.
	\end{itemize}
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$
		\item $u, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I_u, v},\dots,t_n^{I_u, v})\in R^{I_u}$.
		\item $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$.
		\item $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. We denote the set of valid formulas with IQC.
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.
Analogous remarks with regard to validity and satisfiability hold as in the propositional case.

@@

An important step in the embedding will be the elimination of quantifiers via Herbrandization. 
In this process we introduce fresh variables and add additional function symbols to the signature. 
A fresh variable is any variable that does not occur in any of the considered formulas. 
Whenever we add function symbol we implicitly extend the signature by some not previously contained symbol.

@@

Theorem~\ref{thm:herbrand-skolem} follows from Lemmata~\ref{ap1} and~\ref{ap2} stated in the appendix.

@@

\noindent As all we have done is modelling Kripke frames as a first-order theory we directly obtain:

@@

\begin{example}
	Consider the law of excluded middle $$\varphi = (A\to \bot)\vee A$$ which is not intuitionistically valid. Then,
	\begin{align*}
		\varphi^{C} &= K(\varphi)\to ((A\to \bot)\vee A)^u\\
		&= K(\varphi)\to (A\to \bot)^u\vee A^u\\
		&= K(\varphi)\to (\forall u'( u\preceq u' \to A^{u'}\to \bot^{u'})\vee A(u))\\
		&= K(\varphi)\to (\forall u' (u\preceq u' \to A(u')\to \bot)\vee A(u)),
	\end{align*}
and indeed $\varphi^{C}$ admits a counter model with domain $\{u, u'\}$ where $u \preceq u'$, $A(u) = 0, A(u') = 1$.
\end{example}

@@

Of course transforming a propositional formula into a predicate formula is somewhat unsatisfying. As a first step we want to apply Herbrandization. Now trying to apply it to arbitrary formulas presents us with quite a leap in complexity, leading to nested expressions that will make arguments more complicated. We therefore propose a Tseytin-like transformation that produces a formula of a more manageable syntactic form. A similar translation was proposed in~\cite{statman1979intuitionistic}.
\todo{what has been done in the previous work? just the propositional case? just classical logic? did you find a citation for the full Tseytin-like transformation somewhere? If this is new we might add it to the intro.}

@@

\begin{proof}
The claims are verified in a straightforward manner by induction on $\varphi$.
\end{proof}

@@

Then from the previous three Lemmas we get
\todo{as a general rule, I like to finish sentences with a proper grammatical ending, here `:'}

@@

We are now ready to put these two reduction together with our embedding f. Let $\varphi$ be some propositional formula. As a first step we perform the normalization from the last section, i.e. instead of $\varphi$ we consider $$\varphi' = \bigwedge \mathcal S^-(\varphi)\to P_\varphi$$
\todo{here the previous sentence did not finish with a proper grammatical ending as well, I would add `.' after $P_\varphi$}

Recall that since $\varphi$ is quantifier-free each formula $\psi\in\mathcal S^-(\varphi)$ is of one of the forms
$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C,$$
where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u),$$
where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B(k)\wedge C(k))), \forall k(u\preceq k\to (A(k)\wedge (B(k))\to C(k)))$$
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B(k)\vee C(k))), \forall k(u\preceq k\to (A(k)\vee B(k))\to C(k))$$
$$\forall k(u\preceq k\to (\forall l(k\preceq l \to A(l)\to B(l))\to C(k)))$$
with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s)$$
where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
$$\hspace*{-2mm}\forall k(s\preceq k\to A(k)\to (B(k)\wedge C(k))), \forall k(s\preceq k\to (A(k)\wedge (B(k))\to C(k)))$$
$$\hspace*{-2mm}\forall k(s\preceq k\to A(k)\to (B(k)\vee C(k))), \forall k(s\preceq k\to (A(k)\vee (B(k))\to C(k)))$$
$$\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A(f_\psi(k))\to B(f_\psi(k)))\to C(k)),$$
and $f_\psi$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model then we have a counter-model $(M',I')$ where $$M' = \{m\in M|s\preceq m\}$$ and
$$f_\psi^{I'}(u) = \begin{cases}
	f^I_\psi(u), &\text{ iff $u\preceq f^{I}_\psi(u)$,}\\
	u,&\text{ else.}
\end{cases}$$ that is where $s$ is a least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
$$\forall k(A(k)\to (B(k)\wedge C(k))), \forall k((A(k)\wedge B(k))\to C(k))$$
$$\forall k(A(k)\to (B(k)\vee C(k))), \forall k((A(k)\vee B_\psi(k))\to C(k))$$
$$\forall k((A(f_\psi(k))\to B(f_\psi(k)))\to C(k))$$
and $\mathcal F_\to$ denotes the set of formulas of the last kind.

This is as far as the first-order encoding can be simplified. What remains is the elimination of the remaining weak $\forall$-quantifiers.
\todo{delete the last two sentences?}

@@

\begin{definition}
Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^\circ$.
We say $\psi\in\mathcal F_\to$ is \emph{fulfilled} at $u\in M$ iff $A_\psi^I(u)\to B_\psi^I(u)$ is false or $C_\psi^I(u)$ is true. For $\psi\in\mathcal F_\to$ define $$g_\psi : M\to M, u\mapsto\begin{cases}
		u,&\text{ if $\psi$ is fulfilled in $u$,}\\
		f^I_\psi(u),&\text{ else.}		
	\end{cases}$$Define a model $\mathcal M_T = (M_T, I_T)$ as follows:
	\begin{itemize}
		\item $M_T$ is the set of sequences without repetition on $\mathcal F_\to$.
		\item Interpret $\preceq$ as the prefix-order.
		\item We set $$f_\psi^{I_T}(\psi_1\dots\psi_n) = \begin{cases}
			\psi_1\dots\psi_n, &\text{if $\psi$ occurs in $\psi_1\dots\psi_n$,}\\
			\psi_1\dots\psi_n\psi, &\text{else.}			
		\end{cases}$$
		\item For propositional variables $P$, we set $$P^{I_T}(\psi_1\dots \psi_n) = P^I(g_{\psi_n}(\dots(g_{\psi_1}(s^I))\dots)).$$
	\end{itemize}
\end{definition}
\begin{lemma}
	Let $\mathcal M = (M, I)$ be a counter-model to $\mathcal \varphi^\circ$.
	\begin{enumerate}
		\item $\psi$ is fulfilled at $f_\psi^I(u)$ for all $u\in M, \psi\in\mathcal F_\to$.
		\item If $\psi$ is fulfilled at some $u\in M$ then $\psi$ is fulfilled at all $w\geq u$.
	\end{enumerate}

@@

\begin{proof}
\todo{I corrected the proof, please check again.}

	1. If $C^I(u)$ is true then we are done due to persistency. Otherwise $C^I(u)$ is false.
Because $(A^I(f_\psi^I(u))\to B^I(f_\psi^I(u)))\to C^I(u)$ holds, then $A^I(f_\psi^I(u))\to B^I(f_\psi^I(u))$ must be false.

	2. Let $w$ be some element with $w\geq u$.
If $C^I(w)$ is true, we are done. 
Otherwise $C^I(w)$ is false.
Due to persistency $C^I(u)$ is also false.
Because $(A^I(f_\psi^I(u))\to B^I(f_\psi^I(u)))\to C^I(u)$ holds, then $A^I(f_\psi^I(u))\to B^I(f_\psi^I(u))$ must be false, i.e. $A^I(u)$ is true and $B^I(u)$ is false. Then $A^I(w)$ and $A^I(f^I_\psi(w))$ is also true due to persistency.
Because $(A^I(f^I_\psi(w))\to B^I(f^I_\psi(w)))\to C^I(w)$ holds, we now get that  $B^I(f^I(w))$ must be false.
But then due to persistency so is $B^I(w)$ and we have that $\psi$ is fulfilled at $w$.
\end{proof}

Essentially what fulfilment of $\psi$ at $u$ tells us is that having $f_\psi(w) = w$ for all $w\geq u$ works.
\todo{what is meant by `having $f_\psi(w) = w$ for all $w\geq u$ works`'? Reformulate the sentence.}
With this lemma in hand showing that $(M_T, I_T)$ is a counter-model to $\varphi^\circ$ is a straightforward check of definitions.

@@

\begin{example}
	Consider
	$$\mathcal S = \{(A\to B)\to C, (B\to A)\to D, (A\wedge B)\to \bot, (C\vee D)\to E\}$$and $\varphi = \bigwedge S\to E$ which has the Kripke counter-model, depicted below,
	\begin{center}
		\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
			\node (center) {};
			\node[squarednode]      (right)   [right=of center] {$B, C$};
			\node[squarednode]      (left)    [left=of center] {$A, D$};
			\node[squarednode]      (lower)       	[below=of center] {};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left.south east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right.south west);			
		\end{tikzpicture}
	\end{center}
	\vspace*{-.3cm}where at each node the true propositions are indicated.
%	
There is a corresponding classical counter-model $\mathcal M = (M, I)$ to $\varphi^\circ$ with $M = \{u, u_l, u_r\}$, $A^{I}(l) = D^I(l) = B^I(r) = C^I(r) = 1$ and $0$ else.
%
Denoting $\psi_1 := (A\to B)\to C$ and $\psi_2 := (A\to B)\to C$ \todo{I guess this should be $\psi_2 := (B\to A)\to D$}, this corresponds to a transformed counter-model $\mathcal M_T = (M_T, I_T)$ of $\varphi^\circ$ with $M_T = \{\epsilon, \psi_1, \psi_2, \psi_1\psi_2, \psi_2\psi_1\}$ and interpretation as presented below:
	\begin{center}
		\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
			\node (center) {};
			\node[squarednode]      (right1)   [right=of center] {$B, C$};
			\node[squarednode]      (right2)   [above=of right1] {$B, C$};
			\node[squarednode]      (left1)    [left=of center] {$A, D$};
			\node[squarednode]      (left2)    [above=of left1] {$A, D$};
			\node[squarednode]      (lower)       	[below=of center] {};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left1.south east) node [midway, below left] {$f_{\psi_1}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right1.south west) node [midway, below right] {$f_{\psi_2}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (left1.north) -- (left2.south) node [midway, right] {$f_{\psi_2}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (right1.north) -- (right2.south) node [midway, left] {$f_{\psi_1}$};
			\draw[-{Stealth[length=3mm, width=3mm]}] (left1.south west) to [out=225, in=135, loop, looseness=3] node [left] {$f_{\psi_1}$} (left1.north west);		
			\draw[-{Stealth[length=3mm, width=3mm]}] (right1.south east) to [out=315, in=45, loop, looseness=3] node [right] {$f_{\psi_2}$} (right1.north east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (left2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (left2.north east);
			\draw[-{Stealth[length=3mm, width=3mm]}] (right2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (right2.north east);		
		\end{tikzpicture}
	\end{center}
\end{example}

So we know that $\varphi^\circ$ is valid iff it is valid for structures that have as a domain the sequences without repetition over $\mathcal F_\to$, ordered by the prefix-relation and $$s^I = \epsilon, f_\psi^I(x) = \begin{cases}
	x, &\text{ if $\psi$ occurs in $x$,}\\
	x, \psi&\text{ otherwise.}
\end{cases}$$ Now we can replace all $\forall$-quantifiers by enumerating all the ground terms and finally all distinct ground instances of relations by new propositional variables yielding a CPC formula. This gives us the following translation:
